---
title: "Scraping-HW-1"
author: "Gyebnar Daniel"
date: '2021 11 14 '
output:
  prettydoc::html_pretty:
    theme: cayman
---
### Task description

I scraped imdb website searching for "James Bond" related content.

I used for loops to extract selected variables within the infosheet of each observation - this allowed my to handle missing data that otherwise was skipped, resulting in different vector length

I extracted the following variables
- title
- year
- rating
- genre
- runtime
- description

### Importing libraries
```{r}
rm(list=ls())

library(rvest)
library(data.table)
library(xml2)
```

### Creating the function
```{r}
get_one_page <- function(url) {
  
  link <- read_html(url)
  
  #getting the details for each movie
  detail <- link %>% html_nodes(".mode-detail")
  
  #getting titles
  titles <- c()
  for (i in detail){
    titles <- c(titles, i %>% html_nodes(".lister-item-header a") %>% html_text())
  }
  
  #getting year publised
  year <- c()
  temp <- c()
  for (i in detail){
    if( length(i %>% html_nodes(".lister-item-header span") %>% html_text()) == 0 ){
      year <- c(year, "")
    } else {
      temp <- i %>% html_nodes(".lister-item-header span") %>% html_text()
      year <- c(year, temp[2])
    }
  }
  length(year)
  
  # getting ratings and filtering out where there is no rating
  rating <- c()
  for (i in detail){
    
    if( length(i %>% html_nodes(".ratings-imdb-rating strong") %>% html_text()) == 0 ){
      rating <- c(rating, "")
    }
    else {rating <- c(rating, i %>% html_nodes(".ratings-imdb-rating strong") %>% html_text())
    }
  }
  rating
  
  # getting runtime
  runtime <- c()
  for (i in detail){
    if( length(i %>% html_nodes(".runtime") %>% html_text()) == 0) {
      runtime <- c(runtime, "")
    }
    else {runtime <- c(runtime,i %>% html_nodes(".runtime") %>% html_text())
    }
  }
  
  # getting description
  description <- c()
  for (i in detail) {
    if( length(i %>% html_nodes(".ratings-bar+ p") %>% html_text()) == 0) {
      description <- c(description, "")
      break()
    }
    if( grepl(c("Add a Plot"), c(i %>% html_nodes(".ratings-bar+ p") %>% html_text())) ) {
      description <- c(description, "")
    }
    else {description <- c(description, i %>% html_nodes(".ratings-bar+ p") %>% html_text())
    }
  }
  
  # getting genre
  genre <- c()
  for (i in detail) {
    if( length(i %>% html_nodes(".genre") %>% html_text()) == 0) {
      genre <- c(genre, "")
      break()
    } else {
    genre <- c(genre, i %>% html_nodes(".genre") %>% html_text())
    }
  }
  
  return(data.frame("Title"=titles, "Year"=year, "Rating"=rating, "Genre"=genre, "Runtime"=runtime, "Desc"=description))
  
}

```


### Getting the links for page 3-5
```{r}
all_links <- paste0("https://www.imdb.com/search/keyword/?keywords=james-bond&ref_=kw_nxt&sort=moviemeter,asc&mode=detail&page=", 3:5)

```

### Creating the final dataframe
```{r}
list_of_dfs <- lapply(all_links, get_one_page)
final_df <- rbindlist(list_of_dfs)
```

### Result
```{r, echo=FALSE}
library(kableExtra)
final_df[1:5,] %>% 
  kbl() %>% 
  kable_classic(full_width=F)
